Thank you, next: partner turnover elevates benefits of mutualism for an ant-tended plant

### 2023-09-29 Manuscript/ant_cactus_AmNat_Ali.tex
Update ant_cactus_AmNat_Ali.tex

\section*{Methods}
\subsection*{Study System}

@@

%% Survival Model
%\begin{figure}[h]
%	\includegraphics[width=0.95\linewidth]{surv_panels.png}
%	\caption{asdasdf}
%	\label{fig:surv}
%\end{figure}
Plants tended by \texit{C. opuntiae} ants experienced significantly higher mean survival rates than \textit{L. apiculatum} tended plants ($p = 2.908 \times 10^{-14}$), plants tended by other ants ($p = 4.488 \times 10^{-14}$), and vacant plants ($p = 2.2 \times 10^{-16}$) \cite{fig:surv}. 
These \textit{C. opuntiae} plants have the highest mean survival at small sizes before reaching a mean survival rate of about 100\% when medium to large.
Plants tended by \textit{L. apiculatum} experienced similar mean survival rates to plants tended by other ants and vacant plants.
\textit{L. apiculatum} tended plants and other tended plants reached a mean survival rate of nearly 100\% by medium sizes, with other tended plants reaching this rate slower. 
Vacant plants never reach mean survival rates of 100\%.

@@

%% Ant Transition Rates
% previously vacant
Plants that were previously vacant will most likely remain vacant until large. 
These plants have significantly higher probabilities of being vacant rather than becoming tended  by \textit{C. opuntiae}, \textit{L. apiculatum}, or other ants (respectively, $p = 2.2 \times 10^{-16}$, $p = 2.2 \times 10^{-16}$, and $p = 2.2 \times 10^{-16}$).
The probability of previously vacant plants becoming tended by \texit{L. apiculatum} ants is significantly higher than the probabilities of becoming tended by \textit{C. opuntiae} or other ants (respecitvely, $p = 3.83 \times 10^{-14}$, $p = 2.2 \times 10^{-16}$).
The probability of previously vacant plants becoming tended by other ants is significantly lower than the probability of becoming tended by \textit{C. opuntiae} ($p = 0.00227$).

@@

@@

%%%%%%%%%%%%%%%%%%%%%
% Statement of Authorship
%%%%%%%%%%%%%%%%%%%%%
% This section should also be commented out while your MS is undergoing
% double-blind review. The specifics should of course be adapted to
% your paper, but the paragraph below gives some hints of possible
% contributions.

@@

% I am creating a table here to include all parameter estimations and descriptions
  \begin{table}[]
  \begin{tabular}{l|l|l}
    \textbf{Parameter} & \textbf{Median ($95\%$ CI)} & \textbf{Prior Distribution} \\
    \hline
    %% Growth Parameters
    growth xi intercept vacant $\Beta_{01}^g$ & -5.210899 (-5.686865, -5.491787) & \\
    growth xi intercept other $\Beta_{02}^g$ & -5.8288 (-5.956217, 1.766021) & \\
    growth xi intercept \textit{C. opuntiae} $\Beta_{03}^g$ & -4.529523 (-6.0770390, 0.1222112) & \\
    growth xi intercept \textit{L. apiculatum} $\Beta_{04}^g$ & -5.106802 (-5.4499944, 0.5453901) & \\
    growth xi size dependent vacant $\Beta_{11}^g$ & & \\
    growth xi size dependent other $\Beta_{12}^g$ & & \\
    growth xi size dependent \textit{C. opuntiae} $\Beta_{13}^g$ & & \\
    growth xi size dependent \textit{L. apiculatum} $\Beta_{14}^g$ & & \\
    growth omega intercept $\omega_0^g$ & & \\
    growth omega size dependent $\omega_1^g$ & & \\
    growth alpha intercept $\alpha_0^g$ & & \\
    growth alpha size dependent $\alpha_1^g$ & & \\
    \hline
    %% Germination Parameters
    1-year germination intercept $\alpha^{\gamma_1}$ & -5.144627 (-5.370185, -4.966587) & \\
    2-year germination intercept $\alpha^{\gamma_2}$ & -6.155088 (-6.417991, -5.786996) & \\
    \hline
    %% Survival Parameters
    survival intercept vacant $\Beta_{01}^s$ & 0.46375959 (0.07778875, 0.86267803) & \\
    survival intercept other $\Beta_{02}^s$ & 0.2677732 (-1.7939375, 2.5857164) & \\
    survival intercept \textit{C.opuntiae} $\Beta_{03}^s$ & 2.2690061 (0.7347587, 3.9967755) & \\
    survival intercept \textit{L. apiculatum} $\Beta_{04}^s$ & 0.0538502 (-1.0054015, 1.3153753) & \\
    survival size dependent vacant $\Beta_{11}^s$ & 0.86267803 (0.2696006, 0.3217293) & \\
    survival size dependent other $\Beta_{12}^s$ & 0.4387909 (0.1953732, 0.7325813) & \\
    survival size dependent \textit{C. opuntiae} $\Beta_{13}^s$ & 0.28392994 (0.08742771, 0.47423484) & \\
    survival size dependent \textit{L. apiculatum} $\Beta_{14}^s$ & 0.5150193 (0.5150193, 0.6492092) & \\
    \hline
    %% Probability of Flowering Parameters
    flowering intercept $\Beta_0^f$ & -4.611414 (-5.119275, -4.082511) & \\
    flowering size dependent $\Beta_1^f$ & 0.5693555 (0.5239602, 0.6104472) & \\
    \hline
    %% Floral Viability Parameters
    viability intercept vacant $\Beta_01^v$ & 1.0930266 (0.5002784, 1.6629479) & \\
    viability intercept other $\Beta02^v$ & 1.1102242 (0.5073163, 1.7414692) & \\
    viability intercept \textit{C. opuntiae} $\Beta_03^v$ & 1.3605548 (0.7372043, 1.9359609) & \\
    viability intercept \textit{L. apiculatum} $\Beta_04^v$ & 2.023599 (1.461603, 2.534776) & 
  \end{tabular}
  \end{table}
\bigskip{}
\\
\end{table}

>>>>

\textsc{\textsc{%\section*{Methods}
\subsection*{Study System}

@@

%% Survival Model
%\begin{figure}[h]
%	\includegraphics[width=0.95\linewidth]{surv_panels.png}
%	\caption{asdasdf}
%	\label{fig:surv}
%\end{figure}
Plants tended by \textit{C. opuntiae} ants experienced significantly higher mean survival rates than \textit{L. apiculatum} tended plants ($p = 2.908 \times 10^{-14}$), plants tended by other ants ($p = 4.488 \times 10^{-14}$), and vacant plants ($p = 2.2 \times 10^{-16}$) \cite{fig:surv}. 
These \textit{C. opuntiae} plants have the highest mean survival at small sizes before reaching a mean survival rate of about 100\% when medium to large.
Plants tended by \textit{L. apiculatum} experienced similar mean survival rates to plants tended by other ants and vacant plants.
\textit{L. apiculatum} tended plants and other tended plants reached a mean survival rate of nearly 100\% by medium sizes, with other tended plants reaching this rate slower. 
Vacant plants never reach mean survival rates of 100\%.

@@

%% Ant Transition Rates
% previously vacant
Plants that were previously vacant will most likely remain vacant until large. 
These plants have significantly higher probabilities of being vacant rather than becoming tended  by \textit{C. opuntiae}, \textit{L. apiculatum}, or other ants (respectively, $p = 2.2 \times 10^{-16}$, $p = 2.2 \times 10^{-16}$, and $p = 2.2 \times 10^{-16}$).
The probability of previously vacant plants becoming tended by \textit{L. apiculatum} ants is significantly higher than the probabilities of becoming tended by \textit{C. opuntiae} or other ants (respecitvely, $p = 3.83 \times 10^{-14}$, $p = 2.2 \times 10^{-16}$).
The probability of previously vacant plants becoming tended by other ants is significantly lower than the probability of becoming tended by \textit{C. opuntiae} ($p = 0.00227$).

@@

Populations of tree cholla that have no ant partners present have a mean fitness of $\lambda = 0.9895$.
Populations with only one ant partner present (\textit{L. apiculatum}, \textit{C. opuntiae}, or other ants) have a mean fitness of $\lambda = 0.9993$, $\lambda = 0.9853$, and $\lambda = 0.9903$ respectively.
Populations with two ant partners present (\textit{L.apiculatum} and \textit{C. opuntiae}, \textit{L.apiculatum} and other, or \textit{C. opuntiae} and other) have a mean fitness of $\lambda = 1.0035$, $\lambda = 1.004$, and $\lambda = 0.9962$ respectively. 
Populations with all ant partners present have a mean fitness of $\lambda = 1.0039$.
The only partner scenarios where $\lambda > 1$ are when \textit{L. apiculatum} ants are present with any other ant partner.

The means are not the only important result.
We used bayesian modeling, so each of these $\lambda$ estimations has a distribution rather than a single estimate.
By subtracting one of these distributions from the other, the difference from 0 tells us how much larger or smaller the distributions are with a percent confidence. 
% single partners
We are 52\% confident that having \textit{C. opuntiae} partners only leads to a lower $\lambda$ than having no partners, indicating these are actually parasites rather than mutualists as has long been suggested.
We are 56\% and 84\% confident that having other ants or \textit{L. apiculatum} ants respectively as the only partner leads to a higher $\lambda$ than having no partners.
\textit{L. apiculatum} ants are the best single partner for tree cholla populations, as they lead to the highest population fitness with a single partner.
% two partners

% all partners

@@

%%%%%%%%%%%%%%%%%%%%
 Statement of Authorship
%%%%%%%%%%%%%%%%%%%%
 This section should also be commented out while your MS is undergoing
 double-blind review. The specifics should of course be adapted to
 your paper, but the paragraph below gives some hints of possible
 contributions.}}

@@

%% I am creating a table here to include all parameter estimations and descriptions
%  \begin{table}[]
%  \begin{tabular}{l|l|l}
%    \textbf{Parameter} & \textbf{Median ($95\%$ CI)} & \textbf{Prior Distribution} \\
%    \hline
%    %% Growth Parameters
%    growth xi intercept vacant $\Beta_{01}^g$ & -5.210899 (-5.686865, -5.491787) & \\
%    growth xi intercept other $\Beta_{02}^g$ & -5.8288 (-5.956217, 1.766021) & \\
%    growth xi intercept \textit{C. opuntiae} $\Beta_{03}^g$ & -4.529523 (-6.0770390, 0.1222112) & \\
%    growth xi intercept \textit{L. apiculatum} $\Beta_{04}^g$ & -5.106802 (-5.4499944, 0.5453901) & \\
%    growth xi size dependent vacant $\Beta_{11}^g$ & & \\
%    growth xi size dependent other $\Beta_{12}^g$ & & \\
%    growth xi size dependent \textit{C. opuntiae} $\Beta_{13}^g$ & & \\
%    growth xi size dependent \textit{L. apiculatum} $\Beta_{14}^g$ & & \\
%    growth omega intercept $\omega_0^g$ & & \\
%    growth omega size dependent $\omega_1^g$ & & \\
%    growth alpha intercept $\alpha_0^g$ & & \\
%    growth alpha size dependent $\alpha_1^g$ & & \\
%    \hline
%    %% Germination Parameters
%    1-year germination intercept $\alpha^{\gamma_1}$ & -5.144627 (-5.370185, -4.966587) & \\
%    2-year germination intercept $\alpha^{\gamma_2}$ & -6.155088 (-6.417991, -5.786996) & \\
%    \hline
%    %% Survival Parameters
%    survival intercept vacant $\Beta_{01}^s$ & 0.46375959 (0.07778875, 0.86267803) & \\
%    survival intercept other $\Beta_{02}^s$ & 0.2677732 (-1.7939375, 2.5857164) & \\
%    survival intercept \textit{C.opuntiae} $\Beta_{03}^s$ & 2.2690061 (0.7347587, 3.9967755) & \\
%    survival intercept \textit{L. apiculatum} $\Beta_{04}^s$ & 0.0538502 (-1.0054015, 1.3153753) & \\
%    survival size dependent vacant $\Beta_{11}^s$ & 0.86267803 (0.2696006, 0.3217293) & \\
%    survival size dependent other $\Beta_{12}^s$ & 0.4387909 (0.1953732, 0.7325813) & \\
%    survival size dependent \textit{C. opuntiae} $\Beta_{13}^s$ & 0.28392994 (0.08742771, 0.47423484) & \\
%    survival size dependent \textit{L. apiculatum} $\Beta_{14}^s$ & 0.5150193 (0.5150193, 0.6492092) & \\
%    \hline
%    %% Probability of Flowering Parameters
%    flowering intercept $\Beta_0^f$ & -4.611414 (-5.119275, -4.082511) & \\
%    flowering size dependent $\Beta_1^f$ & 0.5693555 (0.5239602, 0.6104472) & \\
%    \hline
%    %% Floral Viability Parameters
%    viability intercept vacant $\Beta_01^v$ & 1.0930266 (0.5002784, 1.6629479) & \\
%    viability intercept other $\Beta02^v$ & 1.1102242 (0.5073163, 1.7414692) & \\
%    viability intercept \textit{C. opuntiae} $\Beta_03^v$ & 1.3605548 (0.7372043, 1.9359609) & \\
%    viability intercept \textit{L. apiculatum} $\Beta_04^v$ & 2.023599 (1.461603, 2.534776) & 
%  \end{tabular}
%  \end{table}
%\bigskip{}
%\\
%\end{table}
